\documentclass[letterpaper, roman]{moderncv}

% theme
\moderncvtheme[blue]{classic}

% fonts
\usepackage{times}
\renewcommand{\sfdefault}{\rmdefault}

% character encoding
\usepackage[utf8]{inputenc}

% adjust page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths

% web links
%\usepackage{hyperref}

% personal data
\firstname{Connor}
\familyname{Brubaker}
\address{College Station, TX}{}
\mobile{(737) 217 - 3632}
\email{brubaker@tamu.edu}
\extrainfo{\homepagesymbol\href{https://connorbrubaker.github.io}{connorbrubaker.github.io}}

\begin{document}
    \maketitle
    
    % education
    \section{Education}
    \cventry{2020--2025}{Ph.D. in Statistics}{Texas A\&M University}{College Station, TX}{}{}
    \cventry{2016--2019}{B.S. in Mathematics}{The University of Texas at Austin}{Austin, TX}{GPA: 3.76}{}

    % professional experience
    \section{Professional Experience}
    \cventry{12/2019--7/2020}{Research Scientist Associate}{Applied Research Laboratories}{Austin, TX}{}{
        \begin{itemize}
            \item Implemented open source deep learning algorithms for object detection and tracking in Python.
            \item Researched and developed algorithms for high-dimensional latent clustering in TensorFlow for Python.
            \item Worked with a team to create educational materials for a site course in machine learning.
        \end{itemize}
    }

    \cventry{5/2019--8/2019}{Data Science Intern}{Alerian}{Dallas, TX}{}{
        \begin{itemize}
            \item Transformed website traffic data into a clear and concise report on the value of the company's advertising spending using time series forecasting and change point detection. 
            \item Effectively sumamrized and communicated statistical analyses to company executives.
            \item Improved the accuracy and execution time for data operations by automating data update and population procedures in Excel VBA.
        \end{itemize}
    }

    % teaching experience
    \section{Teaching Experience}
    \cventry{8/2021--Present}{Graduate Assistant Lecturer}{Texas A\&M University}{College Station, TX}{}{
        \begin{itemize}
            \item Instructed and lead students in the fundamentals of descriptive and inferential statistics.
            \item Rendered several hours per week for individual student tutoring.
            \item Prepared lesson plans, evaluation plans, and wrote and conducted exams.
        \end{itemize}
    }

    \cventry{8/2020--8/2021}{Graduate Teaching Assistant}{Texas A\&M University}{College Station, TX}{}{
        \begin{itemize}
            \item Rendered several hours per week for individual student tutoring.
            \item Graded assignments, mid-term, and final exams.
            \item Prepared course materials such as assignment solutions and course notes.
        \end{itemize}
    }

    % projects
    \section{Projects}
    \cventry{2020}{rulsif.ts}{R package}{}{}{
        Implements relative unconstrained least squares importance fitting for change point detection in time series data. Available at \href{https://github.com/connorbrubaker/rulsif.ts}{https://github.com/connorbrubaker/rulsif.ts}.
    }

    % computer languages
    \section{Computer languages and skills}
    \cvlistdoubleitem{R}{Python}
    \cvlistdoubleitem{SQL}{C/C++}
    \cvlistdoubleitem{Java}{Bash/Shell (basics) and Linux}
\end{document}